Excercise

```{r}
library(tidyverse)
```


## What does the below plot show?  Is it useful?  How could it improve?
  
```{r 02-a-few-exercises}
ggplot(mpg, aes(model, manufacturer)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


##  Practice coding the following plots.  Anticipate what the output will look like.  Become familiar with the common components of the plots.

```{r 02-scatterplot-with-mpg}
ggplot(mpg, aes(cty, hwy)) + 
  geom_jitter()
```

```{r 02-scatterplot-with-diamonds}
ggplot(diamonds, aes(carat, price)) + 
  geom_point()
```

```{r 02-scatterplot-with-economics}
ggplot(economics, aes(date, unemploy)) + 
  geom_line()
```

```{r 02-histogram-with-mpg, message=FALSE}
ggplot(mpg, aes(cty)) + 
  geom_histogram()
```

## Exercise: Use faceting to explore the three-way relationship between fuel economy, engine size and number of cylinders.  How does faceting by number of cylinders change your assessment of the relationship between engine size and fuel economy?

## **NOT FACETED BY `cyl`**

```{r 02-not-faceted}
ggplot(mpg, aes(displ, hwy)) +
  geom_point()
```

## **FACETED BY `cyl`**
```{r 02-faceted}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  facet_wrap(~cyl)
```
